The extended light profiles of the Sculptor and Ursa Minor dwarf galaxies: Natural or tidal?

### 2025-09-24 thesis/main.tex
julio sep 1 edits to §1, 2
thesis updates
half-done discussion

\title{
    The extended light profiles of the Sculptor and Ursa Minor dwarf galaxies: Tides or nature?
}
\author{Daniel A. Boyea}

@@

\chapter{The Light Profiles of the Classical Dwarfs}\label{sec:observations}
\input{data}

@@

\chapter{The Effects of Tides}\label{sec:results}
\input{results}

>>>>

\title{
    The extended light profiles of the Sculptor and Ursa Minor dwarf galaxies: Natural or tidal?
}
\author{Daniel A. Boyea}

@@

\chapter{The Light Profiles of the Classical Dwarf Spheroidals}\label{sec:observations}
\input{data}

@@

\chapter{Galactic tidal effects on Sculptor and Ursa Minor}\label{sec:results}
\input{results}
